Parallel-in-time Methods for Particle Simulations

### 2025-02-07 paper/main.tex
Improved abstract

\begin{abstract}
The purpose of this paper is to examine the behavior of parallel-in-time integration in particle simulations, in particular the parareal algorithm, by developing a simple simulator for solar system dynamics that utilizes parallel-in-time integration. We present the results of experiments measuring the run times of the simulation, which we then compare with expectations derived from theory.
\end{abstract}

>>>>

\begin{abstract}
This paper examines parallel-in-time integration, specifically the parareal algorithm, for particle simulations by developing a simple parallel-in-time simulator for solar system dynamics. We present experimental measurements of the simulation run times, which we then compare with expectations derived from theory. Additionally, we explore the behavior of the algorithm with different parameter settings.
\end{abstract}
